Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/framework.tex

\paragraph{Return and discount factor.}
Suitable 
$\deltat$-dependent scalings of the discount factor $\gamma_\deltat$
and the reward $r_\deltat$ are as follows. These definitions fit the discrete case
when $\deltat=1$, and provide well defined, non-trivial returns
and value functions when $\deltat$ goes to $0$.

>>>>

\paragraph{Return and discount factor.}
Suitable 
$\deltat$-dependent scalings of the discount factor $\gamma_\deltat$
and reward $r_\deltat$ are as follows. These definitions fit the discrete case
when $\deltat=1$, and provide well-defined, non-trivial returns
and value functions when $\deltat$ goes to $0$.
